Distinction Centrality Analysis

### 2025-07-20 analysis.qmd
new graphs who dis

```{r}
   b <- make.broker.trees(30)
   c <- lapply(b, distinction.new, norm = FALSE)
```

```{r}
   library(patchwork)
   library(ggraph)
   p.list <- lapply(b, gg)
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Branches =", i+1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1:6)], nrow = 2)
   ggsave(here("Plots", "tree-examples.png"), width = 12, height = 8, units = "in")
```

>>>>

```{r}
   b <- make.broker.trees(30)
   source(here("Functions", "gg.R"))
   p.list <- lapply(b, gg)
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Branches =", i+1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1:6)], nrow = 2)
   ggsave(here("Plots", "tree-examples.png"), width = 12, height = 8, units = "in")
```
